Building an SSI Cluter with GNU/Hurd

### 2019-05-27 libpager/paper.tex
update pseudo code for dealing with lock replies before data returns

\begin{verbatim}
internal_lock_completed: (internal flush variant)
  use alloca() to allocate an array of flags, one set (in a uint8) for each page in current message:
    PAGEIN, UNLOCK, ERROR
  for all pages covered by message:
    [ if this client had WRITE access, print error (should have used m_o_data_return instead of m_o_lock_completed) ]
    if this client isn't on ACCESSLIST, do nothing (m_o_data_return already processed the data)
    if WAITLIST is empty, do nothing (m_o_data_request already called internal_lock_completed)
    else:
      remove client from ACCESSLIST
      if ACCESSLIST is empty but WAITLIST is not:
        if INVALID is not set: set PAGEIN flag
        else (INVALID set): call send_error_to_WAITLIST
          XXX: assumes that ERROR is correctly set whenever INVALID is set

@@

\begin{verbatim}
m_o_data_return: (kernel returning pages)
  (this can not be used in liu of a lock completed message for a WRITE,
     because it doesn't indicate if the kernel still maintains WRITE access)
  npages = length / __vm_page_size;
  pm_entries points to 'npages' entries in pagemap
  lock pager
  ASSERT: this client should be all the page's ACCESSLISTs

>>>>

\begin{verbatim}
internal_lock_completed: (internal flush variant)
  use alloca() to allocate an array of flags, one set (in a uint8) for each page in current message:
    PAGEIN, UNLOCK, ERROR
  for all pages covered by message:
    if this client had WRITE access, do nothing (we're waiting for an m_o_data_return)
    if this client isn't on ACCESSLIST, do nothing (m_o_data_return already processed the data)
    if WAITLIST is empty, do nothing (m_o_data_request already called internal_lock_completed)
    else:
      remove client from ACCESSLIST
      if ACCESSLIST is empty but WAITLIST is not:
        if INVALID is not set: set PAGEIN flag
        else (INVALID set): call send_error_to_WAITLIST
          XXX: assumes that ERROR is correctly set whenever INVALID is set

@@

\begin{verbatim}
m_o_data_return: (kernel returning pages)
  (this can not be used in liu of a lock completed message for revoking WRITE access,
     because it could be spontaneously generated by the kernel, and
     doesn't indicate if the kernel still maintains WRITE access)
  npages = length / __vm_page_size;
  pm_entries points to 'npages' entries in pagemap
  lock pager
  ASSERT: this client should be all the page's ACCESSLISTs
